\begin{acknowledgments}

I thank the National Aeronautics and
Space Administration and the National Science Foundation 
for supporting the research presented in this thesis. 
My work was also supported by collaborative visits funded
by the Cosmology and Astroparticle Student and Postdoc
Exchange Network (CASPEN). Sincerest thanks to the astronomy department at OSU for their generous support through teaching assistantships during my Ph.D. candidacy and defense. 
Thanks to my home department, physics, for all the support that allowed me to find the best fit for a research group for my Ph.D. 
Many thanks to the Ohio Supercomputer Center - what would I do without you, Oakley. 

I am deeply grateful for the opportunity to work as a member of the Connolly group and the ANITA collaboration. I could not ask for a more well-rounded and adventure-filled Ph.D. for which I thank my advisor, Amy Connolly, and Peter Gorham, Jim Beatty, Patrick Allison, David Saltzberg, and Stephanie Wissel, among others. I am grateful for the support and friendship of postdocs Linda Cremonesi, Cosmin Deaconu, and Ben Strutt. 

My sincerest thanks to Connolly group members and alumni, Carl Pfendner, Sam Stafford, Mike Sutherland, Kaeli Hughes, Brian Dailey, among others, for welcoming me into the group and supporting me through the years. Heartfelt thanks to my Ph.D. sibling and office-mate, Brian Clark. I cannot imagine realizing this dream without your friendship, daily support, lunches (including the Qdoba bowl you just brought me to my desk!), and elderberries, Brian. Love you to Antarctica and back! 

I am deeply grateful to Mauricio Bustamante for all his help in learning about Gamma Ray Burst theories and for letting me include in this thesis a previously unpublished, beautiful figure he made. 
Thanks a ton to Mat Page for sharing many useful insights on observing Gamma Ray Bursts. Thank you to everyone at Mullard Space Science Laboratory that helped to arrange my visit there and for showing me around!
Special thanks to Brian Connolly for sharing his expertise in analysis which was very helpful in approaching a problem of removing noise from the ANITA data. 

Special thanks to my teachers and mentors at South Point School and High School back in Kolkata. Many, many teachers there have made me who I am - I will specially mention my high school physics teacher Partha Pratim Roy (the famous PPR) - thank you, Sir. 

I am extremely grateful for a wonderful undergraduate experience at NC State. 
Thank you to everyone there for not only welcoming me to school but to the United States! Special thanks to my amazing professors there: John Blondin, Stephen Reynolds, David Haase, Carla Frohlich, among others. Last but not least, I thank my first research advisor, Leslie Sombers, for giving me a chance to work in her lab as a freshman. That's where I got to be a scientist for the first time!

I thank my family - Ma, Baba, Dada, Mark, and Fuji, for everything. Now, we can move on with our lives. 
Thank you to my friends, especially, my 
best friend Twameka Kumar for being there for me since Nursery.  
Love you all lots.


\end{acknowledgments}