\begin{vita}
%\dateitem{Oct 17, 1990}{Born---Kolkata, India}
\dateitem{June 2011}{Bachelors of Science in Physics and Mathematics, Johns Hopkins University}
\dateitem{Dec 2014}{Master of Science in Physics, The Ohio State University}
% Insert other relevant items here (GTA, etc.)

\begin{publist}

\pubitem{Antoine Camper, Hyunwook Park, \textbf{Stephen J. Hageman}, Greg Smith, Thierry Auguste,
	Pierre Agostini, and Louis F. DiMauro. High relative-phase precision beam duplicator
	for mid-infrared femtosecond pulses. Optics Letters, 44(22):5465-5468, November 2019.}

\pubitem{B. Peters, A. Alfonsov, C. G. F. Blum,\textbf{ S. J. Hageman}, P. M. Woodward, S. Wurmehl, B. Büchner, and F. Y. Yang, “Epitaxial films of Heusler compound Co$_{2}$FeAl$_{0.5}$Si$_{0.5}$ with high crystalline quality grown by off-axis sputtering,” Appl. Phys. Lett. 103, 162404 (2013)}
\pubitem{W. G. Wang, A. Pearse, M. Li, \textbf{S. Hageman}, A. X. Chen, F. Q. Zhu, and C. L. Chien, “Parallel fabrication of magnetic tunnel junction nanopillars by nanosphere lithography,” Scientific Report 3, 1948 (2013)}
\pubitem{W. G. Wang, M. Li, \textbf{S. Hageman}, and C. L. Chien, "Electric-field-assisted switching in magnetic tunnel junctions," Nature Mater. 11, 64 (2012)}
\pubitem{W. G. Wang, \textbf{S. Hageman}, M. Li, S. X. Huang, X. M. Kou, X. Fan, J. Q. Xiao, and C. L. Chien, "Thermal annealing study of magnetoresistance and perpendicular anisotropy in magnetic tunnel junctions based on MgO and CoFeB," Appl. Phys. Lett. 99, 102502 (2011)}


\end{publist}


%\begin{fieldsstudy}
%\majorfield{Physics}
%\onestudy{Particle Astrophysics}{Connolly group} % optional
% Alternatively you can do:
%\end{fieldsstudy}

\end{vita}
